\begin{rSection}{EXPERIENCE}

\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[\tiny$\bullet] #1}
}

\quad\textbf{Underwriting Intern} | \textit{Co-operators. Sovereign General Insurance} \hfill May 2024 - Present\\
\rightline{\textit{Toronto , ON}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\begin{itemize}
    \itemsep -4pt {} \vspace{-1.5em} 
        \item Worked alongside the \textbf{Analytics} and \textbf{BI} team to help improve efficiency and automation.
        \item Developed a D\&O insurance premium rater from scratch. To be used by underwriters and brokers to generate monthly premium estimations based on a company's revenue, industry, employee count, etc. Utilized company databases in \textbf{SQL} and \textbf{object-oriented programming} principles for \textbf{modularity} and \textbf{re-usability}.
        \item Assisted Underwriters with \textbf{analyzing data related to the risk} being underwritten for new business.
        \item Conducted research to procure additional data needed to make determinations on benefits and rates based on my \textbf{risk assessment}.
\end{itemize}

\quad\textbf{IT Analyst} | \textit{Computing and Communication Services. Univ. of Guelph} \hfill Sept 2023 - April 2024\\
 \rightline{\textit{Guelph , ON}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\begin{itemize}
    \itemsep -4pt {} \vspace{-1.5em}
        \item Provided technical troubleshooting, \textbf{IT information and solutions} to clients.
        \item Clients include students, staff, faculty, executives and associates of the university.
        \item Effectively resolved issues relating to \textbf{network connectivity} (wifi-secure, eduroam, Ethernet), \textbf{Microsoft 365 suite}, \textbf{operating systems} (OS), \textbf{PC hardware}, \textbf{virus/malware defects} and more.
        \item Enhanced customer experience by categorizing and documenting customer concerns on help articles available on the official support website.
       %\item Prepared detailed knowledge transfer plans for new trainees and experienced IT associates.
\end{itemize}

% \quad\textbf{Tutor} | \textit{University of California, Merced} \hfill May 2020 - Aug 2022\\
% %\rightline{\textit{Palo Alto , CA}}
% \begin{itemize}
%     \itemsep -4pt {} \vspace{-1.5em}
%         \item Offering students unique perspectives and fundamental intuition to develop critical problem solving techniques
%         \item Processing the sentiment of students raw text responses and segmenting data into actionable insights for the tutoring center to effectively improve student experience and reduce friction for new student acquisition.
% \end{itemize}

% \quad\textbf{Data Analyst Intern} | \textit{RightSkew LLC} \hfill Dec 2018 - Sep 2020\\
% %\rightline{\textit{Merced , CA}}
% \begin{itemize}
%     \itemsep -3pt {} \vspace{-1.5em}
%         \item Developing business reporting and market analysis. 
%         \item SQL reporting and data visualization.
% \end{itemize}

\end{rSection} 


