\begin{rSection}{PROJECTS}

\quad\textbf{Cheese Clicker} | \textit{React JavaScript, HTML/CSS } \hfill May 2024 - July 2024\\
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\begin{itemize}
    \itemsep -4pt {} \vspace{-1.5em}
        \item An interactive online clicker game developed from the ground up using \textbf{JavaScript} and \textbf{HTML/CSS} \\ with \textbf{React} utilization.
        \item Developed skills in \textbf{web development}, React hooks, audio integration, component-based architecture, local \\ storage, animations and more.
\end{itemize}

\quad\textbf{Realistic 8 Ball Pool} | \textit{Full Stack} \hfill Jan. 2024 - April 2024\\
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\begin{itemize}
    \itemsep -4pt {} \vspace{-1.5em} 
        \item A full stack 8-ball pool simulator with \textbf{realistic physics} that allows for a full match to be played between 2 players. Utilizes \textbf{Python}, a \textbf{C} physics library, \textbf{JavaScript}, \textbf{HTML/CSS} and \textbf{SQL}.
        \item Efficiently stored the state of tables, players and shots in an SQL database which is accessed and handled by a Python web server.
\end{itemize}

\quad\textbf{Game Suite} | \textit{Java, jUnit, Object-Oriented Programming } \hfill Oct. 2022 - Dec. 2022\\
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\begin{itemize}
    \itemsep -4pt {} \vspace{-1.5em} 
        \item Developed a GUI game suite which allows users to play TicTacToe and Number Scrabble game using \textbf{object-oriented programming pillars} in \textbf{Java}.
        \item Used a \textbf{Docker} image as the development environment which involved the use of 
         \textbf{Gradle} and \textbf{Git} to control compilation and packaging, and the \textbf{jUnit} testing framework to maintain a industry level coding environment.
\end{itemize}



% \item \textbf{Realistic 8-Ball Pool} | {A full stack billiards (8 ball pool) simulator that allows for a full game of pool to be played between 2 players locally. Utilizes Python, C, Javascript, CSS and HTML.}
% \item \textbf{Cheese Clicker} | {An interactive online clicker game developed from the ground up with JavaScript and HTML/CSS with React utilization. }
% \href{https://doi.org/10.1117/12.2633172}{https://doi.org/10.1117/12.2633172} 
% \item \textbf{Game Suite} | {A TicTacToe/Scrabble suite which allows both games to be played. Leveraged object-oriented programming pillars in Java to implement game logic and design/GUI. } 


\end{rSection} 